Back to ``Normal'' for the Disintegrating Planet Candidate KIC 12557548 b

### 2018-05-02 ms.tex
More PCA and periodogram descrip. Also corrected sampling

\begin{figure*}[!hbtp]
\begin{centering}
\includegraphics[width=0.45\textwidth]{images/kepler/secondary_eclipse.pdf}
\caption{No secondary eclipse ( $\lesssim$ 50 ppm) is detected from a phase range of -0.25 to 0.75, even with 17 quarters (4 years) of Kepler Long Cadence data.
Here, the data are binned to orbital phases of 0.1 or 1.5 minutes and errors calculated from the standard error in the mean of the data within a bin.
}\label{fig:secEclipse}
\end{centering}
\end{figure*}

In order to perform some analysis techniques on the data and to study the transit depth behavior, we first create a uniform cleaned two dimensional array of the time series.
We interpolated the Kepler long-cadence data set onto a fixed phase grid with a spacing of 30 minutes and put together all the time series that have no gaps into this two dimensional grid.
This cleaned Kepler long-cadence array is shown in Figure \ref{fig:kepPCA}.

\begin{figure*}[!hbtp]
\begin{centering}
\includegraphics[width=0.49\textwidth]{images/kepler/photometry_riverplot.pdf}
\includegraphics[width=0.49\textwidth]{images/kepler/model_riverplot.pdf}
\includegraphics[width=0.49\textwidth]{images/kepler/residual_riverplot.pdf}
\includegraphics[width=0.49\textwidth]{images/kepler/residual_after_shifted_model.pdf}
\caption{Cleaned Kepler Long-cadence data (Top Left) and model fit (Top Right).
(Bottom Left) The residual is shows some periodic behavior.
(Bottom Right) If we allow for shifting in the model with cross-correlation, the periodic behavior is even stronger.
This is likely an erroneous alias caused by a an early typo in the phase grid of 30 seconds instead of 30 minutes.}\label{fig:riverPlots}
\end{centering}
\end{figure*}

@@

\begin{figure*}[!hbtp]
\begin{centering}
\includegraphics[width=0.49\textwidth]{images/kepler/amplitude_periodogram.pdf}
\caption{Periodogram of the amplitude time series shown in Figure \ref{fig:PCAamp}
Bootstrap error estimates for the 2$\sigma$ and 3$\sigma$ confidence intervals are shown.
The peak at 0.65 days is the orbital period.
The peaks at 153 and 750 days are likely caused by the longer intervals of low disintegration activity.}\label{fig:periodogram}
\end{centering}
\end{figure*}

>>>>

\begin{figure*}[!hbtp]
\begin{centering}
\includegraphics[width=0.45\textwidth]{images/kepler/secondary_eclipse.pdf}
\caption{No secondary eclipse ( $\lesssim$ 50 ppm) is detected from a phase range of -0.25 to 0.75, even with 17 quarters (4 years) of Kepler Long Cadence data.
Here, the data are binned to orbital phases of 0.1 (1.5 minutes) and errors calculated from the standard error in the mean of the data within a bin.
}\label{fig:secEclipse}
\end{centering}
\end{figure*}

In order to perform some analysis techniques on the data and to study the transit depth behavior, we first create a uniform cleaned two dimensional array of the time series.
We interpolated the Kepler long-cadence data set onto a fixed phase grid with a spacing of 15 minutes (to Nyquist sample the 30 minute observation cadence) and put together all the time series that have no gaps into this two dimensional grid.
This cleaned Kepler long-cadence array is shown in Figure \ref{fig:riverPlots}.

\begin{figure*}[!hbtp]
\begin{centering}
\includegraphics[width=0.49\textwidth]{images/kepler/photometry_riverplot.pdf}
\includegraphics[width=0.49\textwidth]{images/kepler/model_riverplot.pdf}
\includegraphics[width=0.49\textwidth]{images/kepler/residual_riverplot.pdf}
\caption{Cleaned Kepler Long-cadence data (Top Left) and model fit (Top Right).
(Bottom) The residual is shows some periodic behavior.
(Bottom Right) If we allow for shifting in the model with cross-correlation, the periodic behavior is even stronger.
This is likely an erroneous alias caused by a an early typo in the phase grid of 30 seconds instead of 30 minutes.}\label{fig:riverPlots}
\end{centering}
\end{figure*}

@@

We also perform PCA along the time axis.
This gives the principal components shown in Figure \ref{fig:PCAtime}.

\begin{figure*}[!hbtp]
\begin{centering}
\includegraphics[width=0.49\textwidth]{images/kepler/pca_time_direction.pdf}
\caption{Principal components for orbital phase when working along the time axis.}\label{fig:PCAtime}
\end{centering}
\end{figure*}

In Figure \ref{fig:ampPeriodogram} we show the periodogram of amplitudes that have peaks at 0.654, 22.9, 153 and 750 days.
The 22.9 day peak is consistent with the \citet{kawahara2013starspots} that shows amplitudes are anti-correlated with

\begin{figure*}[!hbtp]
\begin{centering}
\includegraphics[width=0.49\textwidth]{images/kepler/amplitude_periodogram.pdf}
\caption{Periodogram of the amplitude time series shown in Figure \ref{fig:PCAamp}
Bootstrap error estimates for the 2$\sigma$ and 3$\sigma$ confidence intervals are shown.
The peak at 0.654 days is the orbital period.
The peaks at 153 and 750 days are likely caused by the longer intervals of low disintegration activity.
The 22.9 day peak is consistent with the \citet{kawahara2013starspots} peak that is co-incident with the stellar rotation period.}\label{fig:PCAamp}
\end{centering}
\end{figure*}
